Data Analysis in R: Research & Learning

### 2018-10-24 questions.rmd
update

# Question
#### When I write to the Master, I am writing to my forked copy of the website, correct? 
If Mike is still listed as a collaborator, MY edits are only pushed to my version in my repo, and affect only my copy. If I send a Push request, Mike can pull in my changes IF HE CHOOSES?

# Question
#### Still not sure I know difference between a fork and a branch. 
Branch is an alternative version of a single file, but fork is a copy of the original repo in total. Y/N?

# Question
#### Can I build multiple files in R, then push project to GitHub as a complete repo?
Yep. Found instructions for doing it on this website.
https://cfss.uchicago.edu/git05.html

@@

# Question
#### Having a slight problem with Git on laptop.
I can use my desktop and create repos to Dropbox or local machine from GitHub. Laptop throws in an extra step that seems to corrupt process.

>>>>

# R Code

-----

# Project

-----

# Github
#### When I write to the Master, I am writing to my forked copy of the website, correct? 
If Mike is still listed as a collaborator, MY edits are only pushed to my version in my repo, and affect only my copy. If I send a Push request, Mike can pull in my changes IF HE CHOOSES?

-----

#### Still not sure I know difference between a fork and a branch. 
Branch is an alternative version of a single file, but fork is a copy of the original repo in total. Y/N?

-----

#### Can I build multiple files in R, then push project to GitHub as a complete repo?
Yep. Found instructions for doing it on this website.
https://cfss.uchicago.edu/git05.html

@@

-----

#### Having a slight problem with Git on laptop.
I can use my desktop and create repos to Dropbox or local machine from GitHub. Laptop throws in an extra step that seems to corrupt process.
